### 2022-04-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@6a2b0037727a9b03bf181a2cd910b10aeee05a00 🚀

Chiroptera are an hyperdiverse group, distributed in a large part if the
world, and are an important reservoir for different strains of
betacoronaviruses (Drexler et al., 2014); this has attracted attention
to areas where high diversity of bats can be an important issue for
human health (Calisher et al., 2006). Accordingly, we collected the IUCN
rangemaps for known hosts of betacoronaviruses, to illustrate where
hotspots of host diversity are. These results are presented in Fig xx.a.
As per our current knowledge of which bats are hosts of
betacoronaviruses, these hotspots are primarily South-East Asia, parts
of Europe, and to a lesser extent sub-saharan Africa. Even the subset of
chiroptera that are hosts of betacoronaviruses fits the evolutionary
timeline of the group. Chiropterans can be classified as Microchiroptera
and macrochiroptera, where macrochiroptera have an older history from an
evolutionary perspective compared to macrochiroptera (Springer, 2013;
Teeling et al., 2005). South-East Asia has a high diversity of bats
(Kingston, 2010), and our results show that part of that diversity
includes betacoronavirus hosts. High density of hosts sharing the same
virus (albeit possibly different strains) calls into question the
evolution of the bat antiviral immune system and its co-evolution with
viruses, which may result in distinct immunological responses in
different area, as evidenced in other bat species (Banerjee et al.,
2020)

@@

@@

@@

@@

@@

>>>>

Chiroptera are an hyperdiverse group, distributed in a large part if the
world, and are an important reservoir for different strains of
betacoronaviruses (Drexler et al. 2014); this has attracted attention to
areas where high diversity of bats can be an important issue for human
health (Calisher et al. 2006, Moratelli and Calisher 2015). Accordingly,
we collected the IUCN rangemaps for known hosts of betacoronaviruses, to
illustrate where hotspots of host diversity are. These results are
presented in Fig xx.a. As per our current knowledge of which bats are
hosts of betacoronaviruses, these hotspots are primarily South-East
Asia, parts of Europe, and to a lesser extent sub-saharan Africa. Even
the subset of chiroptera that are hosts of betacoronaviruses fits the
evolutionary timeline of the group. Chiropterans can be classified as
Microchiroptera and macrochiroptera, where macrochiroptera have an older
history from an evolutionary perspective compared to macrochiroptera
(Teeling et al. 2005, Springer 2013). South-East Asia has a high
diversity of bats (Kingston, 2010), and our results show that part of
that diversity includes betacoronavirus hosts. High density of hosts
sharing the same virus (albeit possibly different strains) calls into
question the evolution of the bat antiviral immune system and its
co-evolution with viruses, which may result in distinct immunological
responses in different area, as evidenced in other bat species (Banerjee
et al. 2020).

@@

\leavevmode\hypertarget{ref-Banerjee2020NovIns}{}%
Banerjee, A. et al. 2020. Novel Insights Into Immune Systems of Bats. -
Frontiers in Immunology 11: 26.

@@

\leavevmode\hypertarget{ref-Drexler2014EcoEvo}{}%
Drexler, J. F. et al. 2014. Ecology, evolution and classification of bat
coronaviruses in the aftermath of SARS. - Antiviral Research 101:
45--56.

@@

\leavevmode\hypertarget{ref-Moratelli2015BatZoo}{}%
Moratelli, R. and Calisher, C. H. 2015. Bats and zoonotic viruses: Can
we confidently link bats with emerging deadly viruses? - Memórias do
Instituto Oswaldo Cruz 110: 1--22.

@@

\leavevmode\hypertarget{ref-Springer2013PhyBat}{}%
Springer, M. S. 2013. Phylogenetics: Bats United, Microbats Divided. -
Current Biology 23: R999--R1001.

@@

\leavevmode\hypertarget{ref-Teeling2005MolPhy}{}%
Teeling, E. C. et al. 2005. A Molecular Phylogeny for Bats Illuminates
Biogeography and the Fossil Record. - Science (New York, N.Y.) 307:
580--584.
